---
title: "Analisis Exploratorio"
author: "Ricardo Zamora Mennigke"
date: "3/12/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(devtools)

#find_rtools()
# NOT RUN {
#install.Rtools() # installs the latest version of RTools (if one is needed)
#install.Rtools(TRUE) # if one is needed - asks the user to choose the latest 
# version of RTools to install

#install.Rtools(TRUE, FALSE) # asks the user to choose 
# the latest version of RTools to install 
# (regardless if one is needed)
# install.Rtools(F,F)

# }

library("gpclib")
library("raster")
library("maptools")
library("broom")
library(mapproj)
gpclibPermit()

library(tidyr)
library(plyr)
library(dplyr)
library(readxl)
library(ggplot2)
library(ggthemes)

```

```{r}
setwd("~/Machine Learning/Tesis/Base de datos")
cr <- readRDS("gadm36_CRI_2_sp (2).rds")
cr2<- fortify(cr, region = "HASC_2")
cantones <- read.csv("01_08_CSV_POSITIVOS.csv", header = TRUE) 
head(cantones)
```

```{r}
table(cr2$id)
```


```{r}
#Unir bases
cr_mapa <- merge(cr2, cantones, by.x= "id", by.y="HASC", all.x = TRUE)
#ordenar pol?gonos
ord2<- order(cr_mapa$order)
cr_mapa <- cr_mapa[ord2, ]
```


```{r}
ggplot() +
  geom_polygon(data = cr_mapa, aes(x = long, y = lat, group = group, fill = Total)) +
  coord_map() + ylim(8, NA) + 
  scale_fill_gradient(low = "grey", high = "red", limits = c(0, 25000)) +
  labs(x = NULL, 
       y = NULL, 
       title = "Personas positivos de Covid-19", 
       subtitle = "Acumulado por cantones en Costa Rica al 8 de enero de 2020") +
  theme_void()
```
```{r}
map_theme <- theme(
  axis.title.x = element_blank(),
  axis.text.x  = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y  = element_blank(),
  axis.ticks.y = element_blank(),
  panel.background = element_rect(fill = "white")
)


ggplot(data = cr_mapa, mapping = aes(x = long, y = lat, group = group)) +
  coord_map() + ylim(8, NA) + 
  geom_polygon(aes(fill = Total)) + 
  geom_polygon(data = cr2, fill = NA, color = "black") +
  scale_fill_gradient2(low = "white", high = "green", limits = c(0, 25000)) +
  coord_quickmap() + 
  labs(x = NULL, 
       y = NULL, 
       title = "Personas positivas de Covid-19", 
       subtitle = "Acumulado por cantones en Costa Rica al 8 de enero de 2020") +
  map_theme

```
```{r}
cantones2 <- read.csv("01_08_CSV_FALLECIDOS.csv", header = TRUE) 
head(cantones2)


#Unir bases
cr_mapa <- merge(cr2, cantones2, by.x= "id", by.y="HASC", all.x = TRUE)
#ordenar pol?gonos
ord2<- order(cr_mapa$order)
cr_mapa <- cr_mapa[ord2, ]

```

```{r}
map_theme <- theme(
  axis.title.x = element_blank(),
  axis.text.x  = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y  = element_blank(),
  axis.ticks.y = element_blank(),
  panel.background = element_rect(fill = "white")
)


ggplot(data = cr_mapa, mapping = aes(x = long, y = lat, group = group)) +
  coord_map() + ylim(8, NA) + 
  geom_polygon(aes(fill = Total)) + 
  geom_polygon(data = cr2, fill = NA, color = "black") +
  scale_fill_gradient2(low = "white", high = "red", limits = c(0, 350)) +
  coord_quickmap() + 
  labs(x = NULL, 
       y = NULL, 
       title = "Personas fallecidas de Covid-19", 
       subtitle = "Acumulado por cantones en Costa Rica al 8 de enero de 2020") +
  map_theme
```

```{r}
cantones3 <- read.csv("01_08_CSV_RECUP.csv", header = TRUE) 
head(cantones3)


#Unir bases
cr_mapa <- merge(cr2, cantones3, by.x= "id", by.y="HASC", all.x = TRUE)
#ordenar pol?gonos
ord2<- order(cr_mapa$order)
cr_mapa <- cr_mapa[ord2, ]
```

```{r}
map_theme <- theme(
  axis.title.x = element_blank(),
  axis.text.x  = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y  = element_blank(),
  axis.ticks.y = element_blank(),
  panel.background = element_rect(fill = "white")
)


ggplot(data = cr_mapa, mapping = aes(x = long, y = lat, group = group)) +
  coord_map() + ylim(8, NA) + 
  geom_polygon(aes(fill = Total)) + 
  geom_polygon(data = cr2, fill = NA, color = "black") +
  scale_fill_gradient2(low = "white", high = "blue", limits = c(0, 20000)) +
  coord_quickmap() + 
  labs(x = NULL, 
       y = NULL, 
       title = "Personas recuperadas de Covid-19", 
       subtitle = "Acumulado por cantones en Costa Rica al 8 de enero de 2020") +
  map_theme

```

```{r}
cantones4 <- read.csv("01_08_CSV_ACTIVOS.csv", header = TRUE) 
head(cantones4)


#Unir bases
cr_mapa <- merge(cr2, cantones4, by.x= "id", by.y="HASC", all.x = TRUE)
#ordenar pol?gonos
ord2<- order(cr_mapa$order)
cr_mapa <- cr_mapa[ord2, ]
```

```{r}
map_theme <- theme(
  axis.title.x = element_blank(),
  axis.text.x  = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y  = element_blank(),
  axis.ticks.y = element_blank(),
  panel.background = element_rect(fill = "white")
)


ggplot(data = cr_mapa, mapping = aes(x = long, y = lat, group = group)) +
  coord_map() + ylim(8, NA) + 
  geom_polygon(aes(fill = Total)) + 
  geom_polygon(data = cr2, fill = NA, color = "black") +
  scale_fill_gradient2(low = "white", high = "brown", limits = c(0, 4000)) +
  coord_quickmap() + 
  labs(x = NULL, 
       y = NULL, 
       title = "Casos activos de Covid-19", 
       subtitle = "Acumulado por cantones en Costa Rica al 8 de enero de 2020") +
  map_theme
```

#Problema son 82 cantones

```{r}
library(sf)
library(xlsx)
library(scales)
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r}
to_upper <- function(x) toupper(chartr("áéíóúÁÉÍÓÚ", "aeiouAEIOU", x))


mapa_cantones <- read_sf("datosgeo/geo_data/cantones/cantones.shp")
head(mapa_cantones)
data1 <- read.csv("datos1.csv")
head(data1)
```



```{r}
#data1$Canton <- to_upper(data1$canton )

mapa_cantones3 <- left_join(x = mapa_cantones,
                           y = data1,
                           by = c("cant_nom2"="canton"))



ggplot(data = mapa_cantones3, aes(fill = falle.total.marzo)) +
  geom_sf(color = "black", size = .1) +
  theme_void() +
    scale_fill_viridis_c(labels = comma,
                         trans = "log10",
                       name = "Fallecidos",
                       direction = 1)+
  labs(title = "Fallecidos por COVID-19 en Costa Rica por canton hasta marzo 2021",
       caption = "Fuente: UNED - Ministerio de Salud") +
  theme(legend.position = "bottom",legend.key.width = unit(1,"cm"),
        plot.title = element_text(hjust = .5, size = 14))
```

```{r}
library(ggplot2)

plot_mapa <- ggplot(data = mapa_cantones3) +
  geom_sf(mapping = aes(fill = falle.total.marzo),
          color = "#252525") +
  scale_fill_viridis_c(
    guide = guide_colorbar(
    title.position = "top",
    title.theme = element_text(size = 12)
  )) +
    theme_void() +
  theme(legend.position = "bottom",
        legend.key.width  = unit(2.5,"cm"))
plot_mapa
```

```{r}
GAM <- c("San José", "Escazú", "Desamparados", "Aserrí",
         "Mora", "Goicoechea", "Santa Ana", "Alajuelita",
         "Vázquez de Coronado", "Tibás", "Moravia","Montes de Oca" ,
         "Curridabat","Heredia", "Barva", "Santo Domingo",
         "Santa Bárbara", "San Rafael", "San Isidro", "Belén",
         "Flores", "San Pablo","Cartago", "Paraíso", "La Unión",
         "Alvarado", "Oreamuno" , "El Guarco","Alajuela","Atenas",
         "Poás")
mapa_GAM <- subset(mapa_cantones3, cant_nom2 %in% GAM)
```

```{r}
library(ggplot2)

plot_mapa_gam <- ggplot(data = mapa_GAM) +
  geom_sf(mapping = aes(fill = falle.total.marzo),
          color = "#252525") +
  scale_fill_viridis_c() +
  theme_void() +
  theme(legend.position = "none",
        panel.border = element_rect(color = "black", fill = NA))
plot_mapa_gam

```

```{r}
g1 <- plot_mapa +
  annotation_custom(
    grob = ggplotGrob(plot_mapa_gam),
    ymax = 1056114 ,
    xmax = 480943.3
  ) +
  annotate(geom = "rect",
           xmin =448593.5,
           xmax = 540943.3,
           ymin = 1056114,
           ymax = 1151499,
           fill = NA,
           color = "white")
g1
```
```{r}
library(forcats)
mapa_GAM <- mapa_GAM[!is.na(mapa_GAM$falle.total.marzo),]
g2 <- ggplot(data = mapa_GAM, 
       mapping = aes(y = fct_reorder(cant_nom2,
                                     falle.total.marzo),
                     x = falle.total.marzo)) +
  geom_point(size = 3) +
  geom_segment(aes(x = 0,
                   y = cant_nom2,
                   xend = falle.total.marzo,
                   yend = cant_nom2)) +
 
  theme_minimal() +
  labs(x = "Fallecidos GAM", y = "") +
  theme(text = element_text(size = 14, face = "bold"))
g2
```

```{r}
library(egg)
library(grid)
gl <- list(g1, g2)
grid.arrange(grobs = gl,
             nrow = 1,
             widths = c(2,2),
             layout_matrix = rbind(c(1, 2),c(1, 2)),
             top = textGrob("Fallecidos por COVID-19 cantones del GAM",
                            gp = gpar(fontface = 2,
                                      fontsize = 16),
                            hjust = 0.5,
                            x = 0.5)
             )
```



```{r}
library(ggplot2)

plot_mapa <- ggplot(data = mapa_cantones3) +
  geom_sf(mapping = aes(fill = falle.total.marzo),
          color = "#252525") +
  scale_fill_gradient2(low = "white", high = "red", limits = c(0, 500))+
    theme_void() +
  theme(legend.position = "bottom",
        legend.key.width  = unit(2.5,"cm"))
plot_mapa
```
```{r}
#https://rspatial.org/raster/analysis/index.html
#https://rspatial.org/terra/spatial/index.html
#http://gis.humboldt.edu/OLM/r/Spatial%20Analysis%20With%20R.pdf
#https://spacetimewithr.org/Spatio-Temporal%20Statistics%20with%20R.pdf
#http://carlosreynoso.com.ar/archivos/territorio/Gelfand-Handbook-of-Spatial-Statistics.pdf
```



```{r}
head(mapa_cantones3)
```

```{r}
library(dplyr)
```

```{r}
#### Boxplots for temporal trend
library(ggplot2)
ggplot(mapa_cantones3, aes(x = factor(provincia), y = falle.total.marzo)) +
    geom_boxplot(fill="red", alpha=0.7) + 
    scale_x_discrete() +
    scale_y_continuous(name = "Fallecidos") + 
    theme(text=element_text(size=16), plot.title=element_text(size=18, face="bold")) 

```
```{r}
#### Scatterplot
library(GGally)
ggpairs(mapa_cantones3, c("falle.total.marzo", "posi.total.marzo"))
```
```{r}

to_upper <- function(x) toupper(chartr("áéíóúÁÉÍÓÚ", "aeiouAEIOU", x))


mapa_cantones <- read_sf("datosgeo/geo_data/cantones/cantones.shp")
head(mapa_cantones)
data1 <- read.csv("datos1.csv")
head(data1)
```


```{r}
mapa_cantones <- st_transform(mapa_cantones, crs = "+proj=longlat +ellps=WGS84 +no_defs")
head(mapa_cantones)
```



```{r}
#data1$Canton <- to_upper(data1$canton )

mapa_cantones4 <- left_join(x = mapa_cantones,
                           y = data1,
                           by = c("cant_nom2"="canton"))

```

```{r}
#### Read in the spatial object
library(rgdal)
head(mapa_cantones4)
```


```{r}


library(leaflet)

colours <- colorBin(palette = "YlOrRd", domain = mapa_cantones4$falle.total.marzo)
leaflet(data=mapa_cantones4) %>% 
    addTiles() %>% 
    addPolygons(label = mapa_cantones4$cant_nom2,
                fillColor = ~colours(mapa_cantones4$falle.total.marzo), 
                color="black",
                fillOpacity = 0.7, weight = 1, smoothFactor = 0.5,
                opacity = 1.0) %>%
    addLegend(pal = colours, values = mapa_cantones4$falle.total.marzo, 
              opacity = 1, title="Fallecidos") %>%
    addScaleBar(position="bottomleft")
```

#Spatio temporal patterns
```{r}
library(rgdal)
library(sf)
library(spdep) 
library(tmap)
library(tidyverse)
library(magick)
library(plotly)
library(tmaptools)
library(gridExtra)
```

#checking map
```{r}
qtm(mapa_cantones)
```




```{r}
#### Construct the spatial objects
mapa_cantones4[rowSums(is.na(mapa_cantones4))!=0,]

```
```{r}
test <- st_is_valid(mapa_cantones4,reason=TRUE)
length(which(test!= "Valid Geometry"))
```

#map showing the distribution
```{r}
qtm(mapa_cantones4, "falle.total.marzo")
```
#Queen contiguity weight matrix
```{r}
wm_q <- poly2nb(mapa_cantones4, queen=TRUE)
summary(wm_q)
```

#complete weight matrix

```{r}
str(wm_q)

```

```{r}
st_coordinates(st_centroid(mapa_cantones$geometry))
```


#(ROOK) contiguity based neighbours
```{r}
wm_r <- poly2nb(mapa_cantones4, queen=FALSE)
summary(wm_r)
```

```{r}
class(mapa_cantones)
```

```{r}
# Convert to spatialpointdataframe
spdf_central_cr<-as_Spatial(mapa_cantones)
# compute Rook contiguity weight matrix
wm_r <- poly2nb(spdf_central_cr, queen=FALSE)
# compute Queen contiguity weight matrix
wm_q <- poly2nb(spdf_central_cr, queen=TRUE)

# save coordinates to variable
coords <- coordinates(spdf_central_cr)
head(coords)
```


#Plotting Queen contiguity based neighbours maps
```{r}
plot(mapa_cantones4, border="lightgrey")
#plot(wm_q, coords, pch = 19, cex = 0.6, add = TRUE, col= "red")
plot(wm_q, coordinates(as(mapa_cantones, "Spatial")), pch = 19, cex = 0.6, add = TRUE, col= "red")

```

```{r}
plot(mapa_cantones4, border="lightgrey")
plot(wm_r, coords, pch = 19, cex = 0.6, add = TRUE, col = "red")
```

```{r}
par(mfrow=c(1,2))
plot(mapa_cantones4, border="lightgrey")
plot(wm_q, coords, pch = 19, cex = 0.6, add = TRUE, col= "red", main="Queen Contiguity")
plot(mapa_cantones4, border="lightgrey")
plot(wm_r, coords, pch = 19, cex = 0.6, add = TRUE, col = "red", main="Rook Contiguity")
```

#distance band

```{r}
k1 <- knn2nb(knearneigh(coords))
k1dists <- unlist(nbdists(k1, coords, longlat = TRUE))
summary(k1dists)
```
#fixed distance weight matrix
```{r}
wm_d62 <- dnearneigh(coords, 0, 19577, longlat = TRUE)
wm_d62
```

```{r}
str(wm_d62)
```
#display the structure of the weight matrix
```{r}
table(mapa_cantones4$cant_nom1, card(wm_d62))

```
```{r}
n_comp <- n.comp.nb(wm_d62)
n_comp$nc
```

```{r}
table(n_comp$comp.id)
```

#Plotting fixed distance weight matrix

```{r}
plot(mapa_cantones4, border="lightgrey")
plot(wm_d62, coords, add=TRUE)
plot(k1, coords, add=TRUE, col="red", length=0.08)
```

#adaptive distance weight matrix
```{r}
knn6 <- knn2nb(knearneigh(coords, k=6))
knn6
```
```{r}
str(knn6)

```
#Plotting distance based neighbours
```{r}
plot(mapa_cantones4, border="lightgrey")
plot(knn6, coords, pch = 19, cex = 0.6, add = TRUE, col = "red")
```

#Weights based on IDW
```{r}
dist <- nbdists(wm_q, coords, longlat = TRUE)
ids <- lapply(dist, function(x) 1/(x))
ids
```


#Row-standardised weights matrix
```{r}
rswm_q <- nb2listw(wm_q, style="W", zero.policy = TRUE)
rswm_q
```

```{r}
rswm_q$weights[1]

```

```{r}
rswm_ids <- nb2listw(wm_q, glist=ids, style="B", zero.policy=TRUE)
rswm_ids
```

```{r}
rswm_ids$weights[1]

```

```{r}
summary(unlist(rswm_ids$weights))

```
#Application of Spatial Weight Matrix
```{r}
#Spatial lag with row-standardized weights
#average neighbor fatality value for each polygon
GDPPC.lag <- lag.listw(rswm_q, mapa_cantones4$falle.total.marzo)
GDPPC.lag
```

#Measure of Global Spatial Autocorrelation
#Moran’s I
```{r}
moran.test(mapa_cantones4$falle.total.marzo, listw=rswm_q, zero.policy = TRUE, na.action=na.omit)

```

#local Moran I
```{r}
fips <- order(mapa_cantones4$cant_nom1)
localMI <- localmoran(mapa_cantones4$falle.total.marzo, rswm_q)
head(localMI)
```
```{r}
printCoefmat(data.frame(localMI[fips,], row.names=mapa_cantones4$cant_nom1[fips]), check.names=FALSE)

```
#Mapping the local Moran’s I
```{r}
hunan.localMI <- cbind(mapa_cantones,localMI)

```

```{r}
tm_shape(hunan.localMI) +
  tm_fill(col = "Ii", 
          style = "pretty",
          palette = "RdBu",
          title = "local moran statistics") +
  tm_borders(alpha = 0.5)
```

#Mapping local Moran’s I p-values
```{r}
tm_shape(hunan.localMI) +
  tm_fill(col = "Pr.z...0.", 
          breaks=c(-Inf, 0.001, 0.01, 0.05, 0.1, Inf),
          palette="-Blues", 
          title = "local Moran's I p-values") +
  tm_borders(alpha = 0.5)
```

#joint maps
```{r}
localMI.map <- tm_shape(hunan.localMI) +
  tm_fill(col = "Ii", 
          style = "pretty", 
          title = "local moran statistics") +
  tm_borders(alpha = 0.5)

pvalue.map <- tm_shape(hunan.localMI) +
  tm_fill(col = "Pr.z...0.", 
          breaks=c(-Inf, 0.001, 0.01, 0.05, 0.1, Inf),
          palette="-Blues", 
          title = "local Moran's I p-values") +
  tm_borders(alpha = 0.5)

tmap_arrange(localMI.map, pvalue.map, asp=1, ncol=2)
```




#Monte Carlo Moran’s I
```{r}
set.seed(1234)
bperm= moran.mc(mapa_cantones4$falle.total.marzo, listw=rswm_q, nsim=999, zero.policy = TRUE, na.action=na.omit)
bperm
```

#Visualising Monte Carlo Moran’s I
```{r}
mean(bperm$res[1:999])

```

```{r}
var(bperm$res[1:999])

```

```{r}
summary(bperm$res[1:999])

```

```{r}
hist(bperm$res, freq=TRUE, breaks=20, xlab="Moran I simulado")
abline(v=0, col="red") 
```

#Geary
#Geary C
```{r}
geary.test(mapa_cantones4$falle.total.marzo, listw=rswm_q)

```

#Monte Carlo similation approach of Geary’s C
```{r}
set.seed(1234)
bperm=geary.mc(mapa_cantones4$falle.total.marzo, listw=rswm_q, nsim=999)
bperm
```

#Visualising the Monte Carlo Geary’s C
```{r}
mean(bperm$res[1:999])

```

```{r}
var(bperm$res[1:999])

```

```{r}
summary(bperm$res[1:999])

```

```{r}
hist(bperm$res, freq=TRUE, breaks=20, xlab="Geary C simulado")
abline(v=1, col="red") 
```

#Moran’s I correlogram and plot
```{r}
MI_corr <- sp.correlogram(wm_q, mapa_cantones4$posi.total.marzo, order=6, method="I", style="B")
plot(MI_corr)
```

#Geary’s C correlogram and plot
```{r}
GC_corr <- sp.correlogram(wm_q, mapa_cantones4$posi.total.marzo, order=6, method="C", style="W")
plot(GC_corr)
```

```{r}
scatterMC_wk13 <- moran.plot(mapa_cantones4$falle.total.marzo, 
                             rswm_ids,
                             labels=as.character(mapa_cantones4$cant_nom1),
                             xlab="COVID-19 ratio segun fallecidos por canton en Costa Rica hasta marzo 2021", 
                             ylab="Indice espacial por canton")
```


#INLA

```{r}
library(maptools)
library(spdep)
library(RColorBrewer)
library(lattice)
library(INLA)
library(dplyr)
library(plyr)
library(sqldf)
library(rgdal)

```
#OLS model using the bayesian framework

```{r}
model_list=list().
model_list[[1]]=as.formula(falle.total.marzo~posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano)
model_list[[2]]=as.formula(falle.total.marzo~offset(logExpected)+porcentajeadltmayor+IDH2018+porcentajeurbano)
model_list[[3]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano)
model_list[[4]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(date_num_str, model="rw2") +
                             f(date_num_unstr, model="iid"))
model_list[[5]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(week_num_str, model="rw2") +
                             f(week_num_unstr, model="iid") +
                             f(region_week_num, model="iid"))
model_list[[6]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(week_num_str, model="rw2") +
                             f(week_num_unstr, model="iid") +
                             f(region_int, model="iid", group=week_num_str_int,
                               control.group=list(model="rw2")))
model_list[[7]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(week_num_str, model="rw2") +
                             f(week_num_unstr, model="iid") +
                             f(week_num_unstr_int, model="iid", group=region_int,
                               control.group=list(model="besag", graph=regions.W)))
model_list[[8]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(week_num_str, model="rw2") +
                             f(week_num_unstr, model="iid") +
                             f(region_int, 
                               model="besag", graph=regions.W, 
                               group=week_num_str_int,
                               control.group=list(model="rw2")))
model_list[[9]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(date_num_str, model="rw2") +
                             f(date_num_unstr, model="iid") +
                             f(region_date_num, model="iid"))
model_list[[10]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(date_num_str, model="rw2") +
                             f(date_num_unstr, model="iid") +
                             f(region_int, model="iid", group=date_num_str_int,
                               control.group=list(model="rw2")))
model_list[[11]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(date_num_str, model="rw2") +
                             f(date_num_unstr, model="iid") +
                             f(date_num_unstr_int, model="iid", group=region_int,
                               control.group=list(model="besag", graph=regions.W)))
model_list[[12]]=as.formula(falle.total.marzo~offset(logExpected)+posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano+
                             f(region, model="bym",graph=regions.W) + 
                             f(date_num_str, model="rw2") +
                             f(date_num_unstr, model="iid") +
                             f(region_int, 
                               model="besag", graph=regions.W, 
                               group=date_num_str_int,
                               control.group=list(model="rw2")))

```

```{r}
# Fit models

for (i in 1:length(model_list)){
  model_name=paste0("Model",i)
  model_formula=model_list[[i]]
  assign(model_name,inla(model_formula,
                         family="poisson",
                         control.compute = list(dic=T),
                         quantiles=c(0.025, 0.05, 0.1, 0.5, 0.9, 0.95, 0.975),
                         data=region_data))
  save(list=model_name,file=paste0("Model",i,".rda"))
}

```



#Gaussian
```{r}
fit.us<-inla(falle.total.marzo~posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano, family = "gaussian", data=mapa_cantones4, control.compute = list(dic=T))
summary(fit.us)
```

```{r}
#inla.hpdmarginal(p = .95, fit.us$marginals.fixed$giniz)

```

```{r}
#inla.hpdmarginal(p = .95, fit.us$marginals.fixed$ne_bad)

```

```{r}
#inla.hpdmarginal(p = .95, fit.us$marginals.fixed$isowbz)

```


#poisson
```{r}
fit.us<-inla(falle.total.marzo~posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano, family = "poisson", data=mapa_cantones4, control.compute = list(dic=T))
summary(fit.us)

```

#negative binonmial

```{r}
fit.us<-inla(falle.total.marzo~posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano, family = "nbinomial", data=mapa_cantones4, control.compute = list(dic=T))
summary(fit.us)

#fit.nb_us<-inla(infd03~metro+giniz+hispz+blackz+povz+ne_bad+isowbz, family = "nbinomial",E=e+.0001, data=usdat@data, control.compute = list(dic=T))
#summary(fit.nb_us)
```

```{r}
#fit.pre_u<-inla(falle.total.marzo~posi.total.marzo+porcentajeadltmayor+IDH2018+porcentajeurbano + f(struct, model = "iid"), family = "poisson", data=mapa_cantones4, control.compute = list(dic=T))
#summary(fit.pre_u)
```



